---
title: "How to Get Tests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Get Tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(knitr)
```

> As of January 01, 2026, the use of \`get_tests\_...\` functions have been superseded in favor of the expanded usage of \`get_tests\`. The base \`get_tests\` function has been expanded to accept all arguments from the other \`get_tests\_...\` variations.

The get_tests() function is the primary tool for querying performance data from the Hawkin Dynamics Cloud. In v2.0, this single function replaces all previous variations, providing a unified way to filter by date, athlete, team, group, or test type.

## 1. Basic Usage

The simplest way to use `get_tests()` is to provide a date range. You can use standard date strings (`"YYYY-MM-DD"`) or Unix timestamps.

```{r alltests, eval=FALSE}
library(hawkinR)
hd_connect()

# Call all tests
all_tests <- get_tests()

# Pull all tests from the start of 2023 to present
tests <- get_tests(from = "2023-01-01")
```

## 2. Advanced Filtering

You can combine multiple filters to narrow down your dataset. When multiple filters are provided, the API returns trials that meet **all** criteria.

### Filter by Test Type

To isolate specific movements (e.g., Countermovement Jumps), use the `typeId`.

```{r testTypes, eval=FALSE}
# Pull only CMJ tests
cmj_data <- get_tests(typeId = "7nNduHeM5zETPjHxvm7s")

# Test type argument also excepts type name or abbreviation

# Squat Jump
sj_data <- get_tests(typeId = "SJ")

# Iso tests
iso_data <- get_tests(typeId = "Isometric Test")

```

### Filter by Athletes, Teams, or Groups

First, it is important to remember a few specifics of the HD athlete data structure. All unique entities have unique IDs. This includes athletes, tests types, teams, and groups. Each athlete MUST be a part of a team, but MAY optionally be in a group. Also, athletes can be a part of multiple teams and multiple groups. To see which teams and/or groups an athlete is a part of, you can find this in the data frame returned from `get_athletes`. For more information on this, you can go to the [Getting Started](vignettes/Getting_Started.html) page for specifics.

```{r roster, eval=FALSE}
# Store player info in object called roster. 
# 'inactive' is default to FALSE. Set to TRUE if you want to include inactive athletes.
roster <- get_athletes(inactive = FALSE)
```

```{r rosterResp, echo=FALSE}
roster <- data.frame(
  "id" = c("0kEjAzSLpBwUZc4Yp2Ov", "1E1zYBv0CKbrKnsKz1vj", "1lXEZKkNuNwvMLXiqFRr"),
  "name" = c("Athlete One", "Player Two", "Person Three"),
  "active" = c(TRUE, TRUE, TRUE),
  "teams" = c("09u20ij0dj0", "09u20ij0dj0", "9308dj209dj"),
  "groups" = c("0j20j09jd9ud0j", "0j20j09jd9ud0j,92d2098d02j0", ""),
  "external" = c("AMS:dj0203j0dj,GPS:md029j3209j2","AMS:oin208ju09,GPS:od093j32", "AMS:j029j0jd20j,GPS:0d28j098h3")
)

kable(roster)
```

You can filter for a specific athlete, or an entire cohort using `teamId` or `groupId`. In v2.0, these fields accept either a single ID string or a vector of IDs.

```{r specificTestCalls, eval=FALSE}

# Tests By Athlete
athelte <- roster$id[roster$name == "Some Athlete"]
ath_tests <-  get_tests(athleteId = athlete)

# Pull Tests by team
team_ids <- c("team_id_1", "team_id_2")
cohort_data <- get_tests(teamId = team_ids)
```

> It is important to note that test can only be filtered by a singular parameter and a time frame. This means you CAN NOT combine arguments for teams and groups or athlete. Queries can only be made with from, to, and teams OR groups OR athlete.

## 3. The "Sync" Parameter

For developers building local databases, the `sync` parameter allows you to pull data based on when it was **uploaded/modified** rather than when the test occurred. This is essential for Incremental Refresh logic.

```{r syncParams, eval=FALSE}
# Pull everything synced to the cloud in the last 24 hours
last_24h <- as.numeric(Sys.time()) - 86400
new_data <- get_tests(from = last_24h, sync = TRUE)
```

## 4. Data Structure

The returned data frame is automatically processed using internal prep functions (`AthletePrep` and `TestTypePrep`). The columns are organized into four logical sections:

1.  **Trial Info:** Basic trial metadata (ID, timestamp, etc.)

2.  **Test Type Info:** Details about the movement performed.

3.  **Athlete Info:** Details about the athlete who performed the test.

4.  **Metrics:** All performance metrics (Force, Velocity, Power, etc.) with clean names.

## 5. Handling Inactive Data

By default, `get_tests()` only returns trials marked as "Active." If you need to include deleted or hidden trials for auditing purposes, set `includeInactive = TRUE`.

```{r inactiveData, eval=FALSE}
# Include inactive/deleted tests in the response
all_history <- get_tests(from = "2023-01-01", includeInactive = TRUE)
```

------------------------------------------------------------------------

All of the test trials have there own unique ID. This `testId` is what is used in the `get_forcetime` function to call in the raw data from that trial. See [Accessing Force-Time Data of A Test](vignettes/Get_ForceTime_Data.html) for more information.
