---
title: "Accessing Force-Time Data of A Test"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Accessing Force-Time Data of A Test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
editor_options: 
  markdown: 
    wrap: 80
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(knitr)
```

There are many cases in which a researcher or coach would want to access the
high-frequency raw data from a test trial. Just like the calculated metrics, you
can access the time-series data used to create the force plots in your app and
cloud. In v2.0, this process is more secure and integrates directly with the
`HawkinAuth` connection object.

--------------------------------------------------------------------------------

## 1. Establishing a Connection

The first step is always to initialize your session. If you have already stored
your credentials using `hd_auth_store()`, you simply need to connect.

```{r access, eval=FALSE }
library(hawkinR)

# Connect using your default secure profile
hd_connect(region = "Americas")
```

## 2. Locating Test IDs

To pull force-time data, you first need the unique ID of the specific trial. You
can find these IDs by running a query with `get_tests()`.

```{r getMyTests, eval=FALSE}
# Pull recent tests to find a specific trial ID
my_tests <- get_tests(from = "2023-11-01")

# View the first few rows to identify the 'id' column
head(my_tests[, c("id", "athlete_name", "type_name")])
```

## 3. Retrieving Force-Time Series

Once you have the `trialId`, use the `get_forcetime()` function. In v2.0, this
function returns a cleaned data frame where column names are standardized for
easier analysis (e.g., using `time_s`, `force_left`, `force_right`).

```{r testTable, eval=FALSE, echo=TRUE, message=FALSE}
# Select the ID of the specific trial
target_id <- my_tests$id[1]

# Get the raw force-time data
raw_data <- get_forcetime(testId = target_id)

# The result is a data frame ready for plotting or custom analysis
head(raw_data)
```

```{r dataShort, echo=FALSE}

raw_data <- data.frame(
  'time_s' = c(0.001,0.002,0.003,0.004,0.005,0.006,0.007,0.008,0.009,0.01, 0.011, 0.012, 0.013, 0.014, 0.015,0.016,0.017,0.018, 0.019,0.02),
  'force_right' = c(622,622,622,623,622,622,623,622,621,620,620,619,619,619,618,618,619,620,620,620),
  'force_left' = c(564,564,564,564,564,565,566,566,566,566,567,567,568,568,568,568,568,568,569,568),
  'force_combined' = c(1186,1186,1186,1187,1186,1187,1189,1188,1187,1186,1187,1186,1187,1187,1186,1186,1187,1188,1189,1188),
  'velocity_m_s' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  'displacement_m' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  'power_w' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
)

kable(raw_data)
```

## 4. Visualization Example

The data returned by `get_forcetime()` is structured perfectly for ggplot2 or
base R plotting.

```{r fakeCall, eval=FALSE}
library(ggplot2)

ggplot(raw_data, aes(x = time_s)) +
  geom_line(aes(y = force_left, color = "Left")) +
  geom_line(aes(y = force_right, color = "Right")) +
  labs(title = paste("Force-Time Series:", target_id),
       y = "Force (N)",
       x = "Time (s)") +
  theme_minimal()
```

And just like that we have our force-time data. You can do this to with any of
your test types.
